Empirical Evaluation of eval in R

### 2020-08-24 inst/analysis/counts.Rmd
Fix callsite range formatting

```{r callsite-distribution, eval=TRUE}
```{r call-site-table}
eval_callsite_table <-
    package_calls %>%
    mutate(site_count = if_else(site_count <= 10, as.character(site_count), 
                        if_else(site_count <= 50, "11--50",
                        if_else(site_count <= 100, "51--100",
                        if_else(site_count <= 150, "101--150",
                        if_else(site_count <= 200, "151--200",
                        "> 200")))))) %>%
    group_by(site_count) %>%
    summarize(package_count = n()) %>%
    ungroup() %>%
    arrange(match(site_count, c(1:10,"11-50", "51-100", "101-150", "151-200")))

@@

>>>>

```{r callsite-distribution, eval=TRUE}
```{r call-site-table}
eval_callsite_table <-
    package_calls %>%
    mutate(site_count = if_else(site_count <= 10, as.character(site_count), 
                        if_else(site_count <= 50, "11--50",
                        if_else(site_count <= 100, "51--100",
                        if_else(site_count <= 150, "101--150",
                        if_else(site_count <= 200, "151--200",
                        if_else(site_count <= 250, "201--250",
                        if_else(site_count <= 300, "251--300",
                        "> 300")))))))) %>%
    group_by(site_count) %>%
    summarize(package_count = n()) %>%
    ungroup() %>%
    arrange(match(site_count, c(1:10,"11--50", "51--100", "101--150", "151--200", "201--250", "251--300", "> 300")))

@@

```{r core-dependent-own-eval}

```
